From Reversible Programs to \\ Univalent Universes and Back

### 2021-07-09 Pi+/paper/ufin.tex
Fix crefs

% Fourth - explain the tool we use for fixing it
Every type in HoTT is a weak $\infty$-groupoid whose points are the terms of the type, and the (iterated) identity type
gives the (higher) morphisms. The groupoid we are interested in has types as points, type equivalences for 1-cells, and
higher homotopies for higher cells. (See App.~\ref{app:grpdexample} for an example on a 3-element set.) This is the
groupoid structure for the universe type $\UU$, since the identity type on types can be characterised as type
equivalences (by \emph{univalence}). But, we only want to carve out a \emph{subuniverse} of \emph{finite types}, still
satisfying univalence, to get the groupoid structure. In this section, we formally define \emph{univalent subuniverses},
and proceed to construct the particular instance for finite types, $\UFin$ (\Cref{def:ufin}).

@@

  Given two terms $x:A$ and $y:A$, we write $x \id_{A} y$, or simply $x \id y$, for the identity type, which is the type
  of equalities or identifications between them. The identity type is generated by reflexivity $\refl_{x} : x \id_{A} x$,
  and the eliminator for the identity type is given by path induction or the $J$-rule (\Cref{def:path-induction}). This
  construction can be iterated, giving the identity type between two terms of an identity type, repeating ad infinitum.
  Using the iterated identity type for morphisms, each type is equipped with the structure of a weak $\infty$-groupoid,
  where each morphism satisfies groupoid laws only upto a higher one. Given an arbitrary type (or groupoid) $A$, we list
  some laws that are provable using path induction.

@@

The types we are interested in are the finite types. In constructive mathematics, the notion of finiteness is
subtle~\cite{spiwackConstructivelyFinite2010}. We use the notion of Bishop-finiteness: a type is finite if it is merely
equivalent to a finite set (\Cref{def:finite-set} and \Cref{def:isfin}).

>>>>

% Fourth - explain the tool we use for fixing it
Every type in HoTT is a weak $\infty$-groupoid whose points are the terms of the type, and the (iterated) identity type
gives the (higher) morphisms. The groupoid we are interested in has types as points, type equivalences for 1-cells, and
higher homotopies for higher cells. (See App.~\ref{app:grpdexample} for an example on a 3-element set.) This is the
groupoid structure for the universe type $\UU$, since the identity type on types can be characterised as type
equivalences (by \emph{univalence}). But, we only want to carve out a \emph{subuniverse} of \emph{finite types}, still
satisfying univalence, to get the groupoid structure. In this section, we formally define \emph{univalent subuniverses},
and proceed to construct the particular instance for finite types, $\UFin$ (\cref{def:ufin}).

@@

  Given two terms $x:A$ and $y:A$, we write $x \id_{A} y$, or simply $x \id y$, for the identity type, which is the type
  of equalities or identifications between them. The identity type is generated by reflexivity $\refl_{x} : x \id_{A} x$,
  and the eliminator for the identity type is given by path induction or the $J$-rule (\cref{def:path-induction}). This
  construction can be iterated, giving the identity type between two terms of an identity type, repeating ad infinitum.
  Using the iterated identity type for morphisms, each type is equipped with the structure of a weak $\infty$-groupoid,
  where each morphism satisfies groupoid laws only upto a higher one. Given an arbitrary type (or groupoid) $A$, we list
  some laws that are provable using path induction.

@@

The types we are interested in are the finite types. In constructive mathematics, the notion of finiteness is
subtle~\cite{spiwackConstructivelyFinite2010}. We use the notion of Bishop-finiteness: a type is finite if it is merely
equivalent to a finite set (\cref{def:finite-set} and \cref{def:isfin}).
